Supplemental Materials, Methods and Results

### 2022-04-17 supp/Supplemental Materials and Methods.Rmd
fixing up data_long. Removing old code that wasn't working as expected.

      write.csv(data_wide, file = "../output/data/data_final_wide.csv", row.names = FALSE)
##################################
## Re-organise the data frame
##################################
        ################ THIS SHOULD FIX THE DATA_LONG problems
      data_long_t <- data_wide %>%
                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43)) %>% 
                    mutate(type = ifelse(grepl("acute", name), "acute", "acclim")) %>% data.frame()

@@

      data_t1 <- data                                                  %>%
                 dplyr::select(c(1:26, grep("acute_t1", colnames(.)))) %>%
                 filter_if(~is.numeric(.), all_vars(!is.na(.)))        %>% # Filter all the na effect sizes 
                 rename(lnRR_Q10    = lnRR_Q10_acute_t1,       # Rename columns
                        V_lnRR_Q10  = V_lnRR_Q10_acute_t1,
                        lnVR_Q10    = lnVR_Q10_acute_t1,
                        V_lnVR_Q10  = V_lnVR_Q10_acute_t1, 
                        lnCVR_Q10   = lnCVR_Q10_acute_t1,
                        V_lnCVR_Q10 = V_lnCVR_Q10_acute_t1,
                              paper = record_num)            %>%
                 mutate(type = "acute")

      dim(data_t1)

      # Do the same for hot acute
      data_t2 <- data                                                  %>%
                 dplyr::select(c(1:26, grep("acute_t2", colnames(.)))) %>%
                 filter_if(~is.numeric(.), all_vars(!is.na(.)))        %>%  # Filter all the na effect sizes 
                 rename(lnRR_Q10    = lnRR_Q10_acute_t2,
                        V_lnRR_Q10  = V_lnRR_Q10_acute_t2,
                        lnVR_Q10    = lnVR_Q10_acute_t2,
                        V_lnVR_Q10  = V_lnVR_Q10_acute_t2, 
                        lnCVR_Q10   = lnCVR_Q10_acute_t2,
                        V_lnCVR_Q10 = V_lnCVR_Q10_acute_t2,
                              paper = record_num)            %>%
                 mutate(type = "acute")
      dim(data_t2)

      # Now do for the acclimation
      data_acclim <- data                                            %>%
                 dplyr::select(c(1:26, grep("acclim", colnames(.)))) %>%
                 filter_if(~is.numeric(.), all_vars(!is.na(.)))      %>% # Filter all the na effect sizes 
                 rename(lnRR_Q10    = lnRR_Q10_acclim,
                        V_lnRR_Q10  = V_lnRR_Q10_acclim,
                        lnVR_Q10    = lnVR_Q10_acclim,
                        V_lnVR_Q10  = V_lnVR_Q10_acclim, 
                        lnCVR_Q10   = lnCVR_Q10_acclim,
                        V_lnCVR_Q10 = V_lnCVR_Q10_acclim,
                              paper = record_num)            %>%
                 mutate(type = "acclim")
      dim(data_acclim)

      # All these data frames are exactly the same excet that the effect sizes. We've removed NA, so lets bind together

      data_long <- bind_rows(data_t1, data_t2, data_acclim)

>>>>

      write.csv(data_wide, file = "../output/data/data_final_wide.csv", row.names = FALSE)
##################################
## Re-organise the data frame
##################################

@@

        ################ THIS SHOULD FIX THE DATA_LONG problems
      data_long <- data_wide %>%
                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43)) %>% 
                    mutate(type = ifelse(grepl("acute", name), "acute", "acclim")) %>% data.frame()
